\section{General Chair Message}

Welcome to ACL 2023, the 61\textsuperscript{st} Annual Meeting of the Association for Computational Linguistics! The conference will be held in Toronto, Canada, July 9-14, 2023.

Following the succession of the recent conferences in our field, ACL 2023 will adopt a hybrid format. While the impact of Covid has considerably diminished in terms of traveling, obtaining visas to Canada entails a very long process. Moreover, the global economic conditions pose challenges for many individuals to travel to conferences. Recognizing these circumstances, we know many participants may not be able to attend the conference in person. Therefore, we are committed to providing a great virtual platform so everyone has the opportunity to interact with other participants and enjoy the conference. Based on the current registered participants, approximately 26\% have chosen to attend the conference virtually. Whether you join us in person or virtually, we sincerely hope everyone has a remarkable conference experience.


This General Chair’s message is where I express my gratitude to the many individuals who have made enormous contributions to the conference over the past year..

First and foremost, I am grateful for the tremendous efforts by the program chairs: Anna Rogers, Jordan Boyd-Graber, and Naokai Okazaki. The rapid growth of our field is challenging from the perspective of organizing a conference. Program chairs have admirably handled a huge number of submissions and implemented novel review criteria to improve the quality of reviews and the paper decision process. They responded promptly after ChatGPT was launched and provided guidelines for using it in paper writing. Beyond their responsibilities as program chairs, they have assisted me with various other decisions. Their efforts have truly shaped the conference. Also, thanks to all the senior area chairs, area chairs, reviewers, and the best paper committee, whose commitment and dedication made paper review and selection possible.

Next, I would like to thank the entire organizing committee for their service. It has been an honor for me to collaborate with such a dedicated team. This includes:

\begin{itemize}
\item Industry track chairs: Beata Beigman Klebanov, Jason Williams, and Sunayana Sitaram. An addition to this year’s ACL is the introduction of a separate industry track. This is motivated by two factors. First, ACL is held in North America this year (and thus no NAACL), and NAACL has an established tradition of hosting an industry track. Second there was an increasing number of industry track submissions at EMNLP last year from previous years. We hope that a separate industry track can foster the dissemination of research on real-world applications in industry settings. Thanks to the industry track chairs for their efforts in coordinating all the logistics associated with this track.
\item Demo chairs: Alan Ritter, Danushka Bollegala, and Ruihong Huang, who managed demo submissions and accepted 58 demos that will be presented in the main conference.
\item Student research workshop (SRW) chairs: Gisela Vallejo, Vishakh Padmakumar, and Yao Fu, who showed remarkable enthusiasm and dedication in organizing the workshop. They selected 45 papers to be presented in the main conference program. Also thanks to the faculty advisors: Ivan Vulic and Lu Wang, for providing guidance to the SRW chairs and obtaining NSF support for the workshop. 
\item Workshop chairs: Annie Louis, Eduardo Blanco, and Yang Feng, who collaborated with EACL workshop chairs to select 22 workshops, and served as the vital link between the conference and individual workshop organizers.
\item Tutorials chairs: Margot Mieskes, Siva Reddy, and Vivian Chen, who also worked with EACL chairs to select 6 high quality tutorials that cater to the interest and needs of our conference.
\item Ethics chairs: Dirk Hovy and Yonatan Bisk, who checked papers flagged with ethics issues. Thanks for their meticulous work to ensure our papers uphold the ethical standards.
\item Publication chairs: Ryan Cotterell, Chenghua Lin, Jesse Thomason, Lei Shu, and Lifu Huang, who prepared the conference handbook, ensured proper formatting of papers, and produced the conference proceedings.
\item Virtual infrastructure chairs: Jiacheng Xu, Martín Villalba, and Pedro Rodriguez, who worked hard to develop a virtual platform to ensure an engaging conference experience for both in-person and remote participants. They also made various innovations and enhancement on top of the Underline platform, which the conference utilizes. And thanks to Underline for their support in providing the virtual platform and collaborating with us to meet our needs and accommodate our feature requests. 
\item Publicity and social media chairs, Devamanyu Hazarika, Eva Vanmassenhove, and Tong Xu, who communicated and publicized the conference through various social media channels, enhancing the visibility and reach of the conference.
\item Website chairs: Jinho Choi and Zhongyu Wei, who updated and maintained the conference website to keep participants informed.
\item Diversity and inclusion (D\&I) chairs: Daniel Beck, Maryam Fazel-Zarandi, and Nedjma Djouhra Ousidhoum, who arranged support to participants facing financial hardships, and organized a diverse array of activities aimed to promoting diversity and inclusion in our community.
\item Student volunteer chairs: Ayah Zirikly and Tao Yu, who reviewed applications and selected student volunteers for the conference. 
\item Sponsorship chairs: Alla Rozovskaya and Lei Li. Thanks to them and Chris Callison-Burch, the ACL sponsorship Director for their efforts in securing sponsorships and managing the relationship between sponsors and the conference. The generous support from our sponsors has played a crucial role in enabling us to maintain a reasonable registration cost for attendees, and the additional sponsorship for D\&I initiatives helps our commitment to fostering a diverse and inclusive environment.
\item Visa assistance team: Ayana Niwa, Qingwen Liu, Renxiang Zhang, Samridhi Choudhary, and Tao You. Many participants require visas to attend the conference, and we fully understand this lengthy process. This team has been diligently handling visa requests by sending out numerous invitation letters to facilitate visa applications.
\end{itemize}
 
I also want to specially thank Jennifer Rachford, the ACL event director, who handled all the local arrangement for this conference. Though she was relatively new to the role, and often times needed to juggle multiple ACL conferences, she remained well organized, and consistently provided all the necessary information to all members of the organizer committee. Her contributions ensure the success of this conference.

Thanks to previous ACL/EMNLP conference chairs for sharing their knowledge, tips, and best practice on organizing this conference, and ACL Exec for the support they provided throughout the entire planning and execution of this conference. 

Lastly, I extend my appreciation to every participant. Regardless of your role, whether as authors or presenters, workshop organizers, tutorial speakers, student volunteers, session chairs, or simply attendees, your involvement is essential in creating a memorable conference. 

Welcome everyone to the conference!

\vspace{2ex}

ACL 2023 General Chair

Yang Liu (writing assisted by ChatGPT), 

Alexa, Amazon

\clearpage