\section{Organizing Committee}

\subsection*{General Chair:}
\paragraph{} Yang Liu, Amazon, USA. 

\subsection*{Program Chairs:} 
\paragraph{} Anna Rogers, University of Copenhagen, Denmark. 
\paragraph{} Jordan Boyd-Graber, University of Maryland, USA. 
\paragraph{} Naoaki Okazaki, Tokyo Institute of Technology, Japan. 

\subsection*{Workshop Chairs:}
\paragraph{} Annie Louis, Google, UK. 
\paragraph{} Eduardo Blanco, Arizona University, USA. 
\paragraph{} Yang Feng, Chinese Academy of Sciences, China. 

\subsection*{Tutorial Chairs:}
\paragraph{} Margot Mieskes, University of Applied Sciences, Darmstadt, Germany. 
\paragraph{} Siva Reddy, McGill University and Mila, Canada. 
\paragraph{} Vivian Chen, National Taiwan University, Taiwan. 

\subsection*{Demo Chairs:}
\paragraph{} Alan Ritter, Georgia Institute of Technology, USA. 
\paragraph{} Danushka Bollegala, University of Liverpool, UK. 
\paragraph{} Ruihong Huang, Texas A\&M University, USA. 

\subsection*{Industry Track Chairs:}
\paragraph{} Beata Beigman Klebanov, ETS, USA. 
\paragraph{} Jason Williams, Apple, USA. 
\paragraph{} Sunayana Sitaram, Microsoft Research India, India. 

\subsection*{Student Research Workshop Chairs:}
\paragraph{} Gisela Vallejo, University of Melbourne. Australia. 
\paragraph{} Vishakh Padmakumar, New York University, USA. 
\paragraph{} Yao Fu, University of Edinburgh, UK. 

\subsection*{Faculty Advisors to SRW:}
\paragraph{} Ivan Vulic, University of Cambridge, UK. 
\paragraph{} Lu Wang, University of Michigan, USA. 

\subsection*{Ethics Chairs:} 
\paragraph{} Dirk Hovy, Bocconi University, Italy. 
\paragraph{} Yonatan Bisk, Carnegie Mellon University, USA. 

\subsection*{Publication Chairs:}
\paragraph{} Ryan Cotterell, ETH Zürich, Switzerland.
\paragraph{} Chenghua Lin, University of Sheffield, UK. 
\paragraph{} Jesse Thomason, University of Southern California, USA. 
\paragraph{} Lei Shu, Google, USA. 
\paragraph{} Lifu Huang, Virginia Tech, USA

\subsection*{Publicity and Social Media Chairs:} 
\paragraph{} Devamanyu Hazarika, Amazon, USA. 
\paragraph{} Eva Vanmassenhove, Tilburg University, Netherlands. 
\paragraph{} Tong Xu, University of Science and Technology of China, China. 

\subsection*{Website Chairs:}
\paragraph{} Jinho Choi, Emory University, USA. 
\paragraph{} Zhongyu Wei, Fudan University, China.  

\subsection*{Student Volunteer Chairs:}
\paragraph{} Ayah Zirikly, Johns Hopkins University, USA.
\paragraph{} Tao Yu, University of Hong Kong, Hong Kong. 

\subsection*{Virtual Infrastructure Chairs:} 
\paragraph{} Jiacheng Xu, Salesforce, USA. 
\paragraph{} Martín Villalba, Saarland University, Germany. 
\paragraph{} Pedro Rodriguez, Meta, USA.

\subsection*{Diversity and Inclusion Chairs:}
\paragraph{} Daniel Beck, The University of Melbourne, Australia. 
\paragraph{} Maryam Fazel-Zarandi, Meta, USA. 
\paragraph{} Nedjma Djouhra Ousidhoum, University of Cambridge, UK. 

\subsection*{Sponsorship Chairs:}
\paragraph{} Alla Rozovskaya, The City University of New York, USA.
\paragraph{} Lei Li, University of California at Santa Barbara, USA. 

\subsection*{Program Chair Assistant:}
\paragraph{} Youmi Ma, Tokyo Institute of Technology

\subsection*{Visa Assistance Team:}
\paragraph{} Ayana Niwa, Tokyo Institute of Technology, Japan.
\paragraph{} Qingwen Liu, Fudan University, China.
\paragraph{} Renxiang Zhang, Amazon, Canada.
\paragraph{} Samridhi Choudhary, Amazon, Canada.
\paragraph{} Tao You, Fudan University, China.
\subsection*{ACL Event Director:}
\paragraph{} Jennifer Rachford, USA.
